### 2024-06-20 conteudo/tool/functionalities.tex
add example figures

The duplication explorer is the principal functionality of our tool, the functionality purpose is to expose for the user the code duplication
pairs found by our tool. We implement optional filters methods to enable more complex queries, which are described below. A example
of the functionality usage can be found in (ADD FIGURE HERE).

@@

@@

The Function information purpose it to give a more in depth information about a specific function. The functionality inform the user
about the relative path, the function name and the lines the function exist in the code file that the function is contained for the
function that the user is interested and every function that is a duplication of it. As there ca nbe multiple functions with the 
same name in a codebase, we distinguish then by the user providing a pattern string and we use the first function find that match
the pattern. We say that a function matches a pattern if the string formed by the concatenation of the relative path of the 
code file plus the function name. 
A example of the functionality usage can be found in (ADD FIGURE HERE).

@@

The duplication relatory purpose is to give a overview of the input codebase. The functionality extract the information
of how much lines of duplicated code is found per folder in the codebase and present it to the user in a reasonable format. To extract
the information, we use the Code Duplication Database to list the code duplications, and the temporary code to know how much lines of
duplicated code contains in each of the functions. (DO I TALK ABOUT THE TRIE USAGE TO MAINTAIN THE HIERARCHICAL TREE STRUCTURE? I 
THINK NOT). A example of the functionality usage can be found in (ADD FIGURE HERE).

>>>>

The duplication explorer is the principal functionality of our tool, the functionality purpose is to expose for the user the code duplication
pairs found by our tool. We implement optional filters methods to enable more complex queries, which are described below. A example
of the functionality usage can be found in the figure \ref{fig:explorer_ex}.

@@

\begin{figure}
\includegraphics{explorer_example}
\caption{Explorer Example}
\label{fig:explorer_ex}
\end{figure}

@@

The Function information purpose it to give a more in depth information about a specific function. The functionality inform the user
about the relative path, the function name and the lines the function exist in the code file that the function is contained for the
function that the user is interested and every function that is a duplication of it. As there ca nbe multiple functions with the 
same name in a codebase, we distinguish then by the user providing a pattern string and we use the first function find that match
the pattern. We say that a function matches a pattern if the string formed by the concatenation of the relative path of the 
code file plus the function name. 
A example of the functionality usage can be found in the figure \ref{fig:function_ex}.

\begin{figure}
\includegraphics{function_example}
\caption{Function Example}
\label{fig:function_ex}
\end{figure}

@@

The duplication relatory purpose is to give a overview of the input codebase. The functionality extract the information
of how much lines of duplicated code is found per folder in the codebase and present it to the user in a reasonable format. To extract
the information, we use the Code Duplication Database to list the code duplications, and the temporary code to know how much lines of
duplicated code contains in each of the functions. (DO I TALK ABOUT THE TRIE USAGE TO MAINTAIN THE HIERARCHICAL TREE STRUCTURE? I 
THINK NOT). A example of the functionality usage can be found in the figure \ref{fig:relatory_ex}.

\begin{figure}
\includegraphics{relatory_example}
\caption{Function Example}
\label{fig:relatory_ex}
\end{figure}
